Will Kamala Harris will win the 2024 Presidential election

### 2024-11-04 paper/paper.qmd
Grammar edits

In this paper we aim to analyze polling data related to the 2024 election, with a particular emphasis on the swing states. By examining various polls and identifying patterns in voter sentiment, we seek to uncover the factors that may influence voter behavior in these highly contested regions. Our analysis will explore demographic shifts, the impact of key issues, and the level of voter engagement across different swing states. Through a comprehensive statistical approach, we aim to contribute to the understanding of the evolving electoral landscape and provide meaningful insights into the opinions shaping the 2024 presidential election. Using Bayesian regression modeling, we predict the percent of supprt for Kamala Harris in swing states based on pollster and the number of days since she announced her candidacy. Details on our data, variables, and model are discussed further in the Data and Model sections.

@@

Accurate election predictions are important as they help individuals, businesses, and governments anticipate potential shifts in policy, the economy, and international relations. A new president can shape laws, affect the economy, influence international relationships, and address key issues like healthcare, education, and climate change. Knowing which candidate is likely to win enables groups to consider how their plans might align with anticipated policies, encouraging public engagement and participation in the democratic process. It also helps keep people informed and engaged in the political process, making them more likely to vote and participate in democracy in the future.

>>>>

In this paper we aim to analyze polling data related to the 2024 election, with a particular emphasis on the swing states. By examining various polls and identifying patterns in voter sentiment, we seek to uncover the factors that may influence voter behavior in these highly contested regions. Our analysis will explore demographic shifts, the impact of key issues, and the level of voter engagement across different swing states. Through a comprehensive statistical approach, we aim to contribute to the understanding of the evolving electoral landscape and provide meaningful insights into the opinions shaping the 2024 presidential election. Using Bayesian regression modeling, we predict the percent of support for Kamala Harris in swing states based on pollsters and the number of days since she announced her candidacy. Details on our data, variables, and model are discussed further in the Data and Model sections.

@@

Accurate election predictions are important as they help individuals, businesses, and governments anticipate potential shifts in policy, the economy, and international relations. A new president can affect the previously mentioned factors as well as address key issues like healthcare, education, and climate change. Knowing which candidate is likely to win enables groups to consider how their plans might align with anticipated policies, encouraging public engagement and participation in the democratic process. It also helps keep people informed and engaged in the political process, making them more likely to vote and participate in democracy in the future.
